Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-12-28 writing/DraftExposurePaper/DraftExposurePaper.Rmd
continued edit on table

#studies <- c("Davidson 2001", "Atallah 2007", "Kinney 2008", "Zandbergen 2009", "Czajkowski 2010", "Zaharan #2010", "Kruk 2010", "Villarini 2011", "Rezempour 2014", "Currie 2013", "Grabich 2015", "Grabich 2016")
#distance_km <- c("120", "", "Buffer", "25, 30, 60, 75", "30, 60, 100", 
                 "2 counties", "Radial Max Wind", "100-500", "")
#rain_mm <- c("", "2/hr, 48/d", "", "", "", "", "", "", "200-500 (Floyd)")
#wind_kt <- c("", "", "SSWS", "", "SSWS", "", "34, 50, 64", "", "")
#exposure_parameters <- data.frame(studies, distance_km, rain_mm, wind_kt)
#kable(exposure_parameters, "markdown")
```

>>>>

#studies <- c("Davidson 2001", "Atallah 2007", "Kinney 2008", "Zandbergen 2009", "Czajkowski 2010", "Zaharan #2010", "Kruk 2010", "Villarini 2011", "Rezempour 2014", "Currie 2013", "Grabich 2015", "Grabich 2016")
#distance_km <- c("Hurricane Disaster Risk Index (HDRI)", "", "County Center",)
#rain_mm <- c("HDRI", "", "", "2/hr, 48/d", "", "", "", "", "", "", "200-500 (Floyd)")
#wind_kt <- c("HDRI", "", "SSWS", "", "SSWS", "", "34, 50, 64", "", "")
#exposure_parameters <- data.frame(studies, distance_km, rain_mm, wind_kt)
#kable(exposure_parameters, "markdown")
```
